A user-extensible and adaptable parser architecture

### 2008-07-30 doc/logparser-results.tex
Bunch of XXX items added.
Added timing data.

@@

XXX ADD TIMING INFORMATION\@.

@@

CPU         & One dual core 2.40GHz Intel(R) Core(TM)2 CPU, \\
            & with 32KB L1 cache and 4MB L2 cache. \\
RAM         & 2GB 667 MHz DDR RAM\@. \\
Hard disk   & One XXX 232GB SATA disk. \\

@@

In as far as possible the computer was dedicated to the task of gathering
statistics from test runs, and was not used for any other purpose while
test runs were ongoing.

@@

>>>>

USE THE DATA COLLECTED ABOUT NUMBER OF RULES TRIED\@.  MAYBE INCLUDE IN
ORDERINGS SECTION\@?

@@

@@

    CPU         & One dual core 2.40GHz Intel\textregistered{}
                    Core\texttrademark{}2 CPU, \\
                & with 32KB L1 cache and 4MB L2 cache. \\
    RAM         & 2GB 667 MHz DDR RAM\@. \\
    Hard disk   & One Seagate Barracuda 7200 RPM 250GB SATA disk. \\

@@

Parsing all \numberOFlogFILES{} log files in one run took
\input{build/timing-run-include.tex}.

The computer was dedicated to the task of gathering statistics from test
runs, and was not used for any other purpose while test runs were ongoing;
any services not necessary for running the tests were disabled.

@@

I THINK THIS SECTION NEEDS SUBSTANTIAL WORK, IF NOT A RE-WRITE\@.

### 2008-07-30 papers/sgai-2008/paper.tex
Added timing data.

Parsing efficiency is an obvious concern when the parser routinely needs to
parse very large log files.  The server which generated the log files used
in testing this parser accepts approximately 10,000 mails for 700 users a
day.  Median log file size is 50MB, containing 285,000 log lines --- large
scale mail servers would have much larger log files.  When generating the
timing data used in this section, \numberOFlogFILES{} log files (totaling
10.08 GB, \numberOFlogLINEShuman{} log lines) were each parsed 10 times,
the results from the first first run discarded, and the execution time for
the remaining 9 runs averaged.  Saving results to the database was disabled
for the test runs, as that dominates the run time of the program, and the
tests are aimed at measuring the speed of the parser rather than the speed
of the database and the disks the database is stored on.  The computer used
for test runs was a Dell Optiplex 745, equipped with:

@@

In as far as possible the computer was dedicated to the task of gathering
statistics from test runs, and was not used for any other purpose while
test runs were ongoing.

XXX TIMING INFORMATION\@.

XXX TIMING INFORMATION\@.

XXX TIMING INFORMATION\@.

@@

\subsection{Rule Ordering}

@@

At the time of writing there are \numberOFrules{} different rules, with the
top 10\% matching the vast majority of the log lines, and the remaining log
lines split across the other 90\% of the rules in a Power Law distribution
(as shown in fig.~\refwithpage{rule hits graph}).
\showgraph{build/plot-hits}{Hits per rule}{rule hits graph} Assuming that
the distribution of log lines is reasonably steady over time, parser
efficiency should benefit from trying more frequently matching rules before
those which match less frequently.  To test this hypothesis three full test
runs were performed with different rule orderings:

@@

Figure~\refwithpage{Parsing time relative to shuffled} shows the percentage
increase of parsing times for shuffled and reversed rules.  Overall this
optimisation provides a modest but worthwhile performance increase of over
10\%, for a small investment in time and programming.
\showgraph{build/plot-normal-and-reverse-relative-to-shuffle}{Parsing time
relative to shuffled}{Parsing time relative to shuffled}

>>>>

Parsing efficiency is an obvious concern when the parser routinely needs to
parse very large log files.  The server which generated the log files used
in testing this parser accepts approximately 10,000 mails for 700 users a
day.  Median log file size is 50MB, containing 285,000 log lines --- large
scale mail servers would have much larger log files.  When generating the
timing data used in this section, \numberOFlogFILES{} log files (totaling
10.08 GB, \numberOFlogLINEShuman{} log lines) were each parsed 10 times,
the results from the first first run discarded, and the execution time for
the remaining 9 runs averaged.  Saving results to the database was disabled
for the test runs, as that dominates the run time of the program, and the
tests are aimed at measuring the speed of the parser rather than the speed
of the database and the disks the database is stored on.  The computer used
for test runs was a Dell Optiplex 745:

@@

Parsing all \numberOFlogFILES{} log files in one run took
\input{build/timing-run-include.tex}.

The computer was dedicated to the task of gathering statistics from test
runs, and was not used for any other purpose while test runs were ongoing;
any services not necessary for running the tests were disabled.

@@

\newpage
\subsection{Rule Ordering}

@@

At the time of writing there are \numberOFrules{} different rules, with the
top 10\% matching the vast majority of the log lines, and the remaining log
lines split across the other 90\% of the rules in a Power Law distribution
(as shown in fig.~\refwithpage{rule hits graph}).
Assuming that
the distribution of log lines is reasonably steady over time, parser
efficiency should benefit from trying more frequently matching rules before
those which match less frequently.  To test this hypothesis three full test
runs were performed with different rule orderings:

@@

Figure~\refwithpage{Parsing time relative to shuffled} shows the percentage
increase of parsing times for shuffled and reversed rules.  Overall this
optimisation provides a modest but worthwhile performance increase of over
10\%, for a small investment in time and programming.
\showgraph{build/plot-hits}{Hits per rule}{rule hits graph} 
\showgraph{build/plot-normal-and-reverse-relative-to-shuffle}{Parsing time
relative to shuffled}{Parsing time relative to shuffled}
